My title

### 2024-04-19 paper/paper.qmd
discussion

[^1]: An AWP is a powerful but expensive sniper rifle, capable of killing in one shot to the chest
```{r}
#| label: fig-adr
#| fig-cap: Distribution of ADR
#| echo: false
data |> 
  ggplot(aes(x = adr)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ADR", y = "Number of Players") +
  theme_classic()
```

@fig-hs shows the distribution of headshot percentages. A professional *CS* team typically has 4 riflers and 1 AWPer[^1], where riflers aim for the head to do more damage while AWPers are more likely to aim for the chest since it is a larger area and they will kill in a single shot regardless. This could explain why the players are distributed with a left skew.
```{r}
#| label: fig-hs
#| fig-cap: Distribution of Headshot Percentage
#| echo: false
data |> 
  ggplot(aes(x = hs)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Headshot %", y = "Number of Players") +
  theme_classic()
```
@fig-rounds shows the total number of rounds played.
```{r}
#| label: fig-rounds
#| fig-cap: Number of rounds played
#| echo: false
data |> 
  ggplot(aes(x = rounds)) +
  geom_histogram(binwidth = 1000) +
  labs(x = "Rounds Played", y = "Number of Players") +
  theme_classic()
```

@@

## Impacts of an individual on team performance

@@

Weaknesses and next steps should also be included.

>>>>

```{r}
#| label: fig-adr
#| fig-cap: Distribution of ADR
#| echo: false
data |> 
  ggplot(aes(x = adr)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ADR", y = "Number of Players") +
  theme_classic()
```

@fig-hs shows the distribution of headshot percentages. A professional *CS* team typically has 4 riflers and 1 AWPer[^1], where riflers aim for the head to do more damage while AWPers are more likely to aim for the chest since it is a larger area and they will kill in a single shot regardless. This could explain why the players are distributed with a left skew.
[^1]: An AWP is a powerful but expensive sniper rifle, capable of killing in one shot to the chest
```{r}
#| label: fig-hs
#| fig-cap: Distribution of Headshot Percentage
#| echo: false
data |> 
  ggplot(aes(x = hs)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Headshot %", y = "Number of Players") +
  theme_classic()
```
@fig-rounds shows the total number of rounds played.
```{r}
#| label: fig-rounds
#| fig-cap: Number of rounds played
#| echo: false
data |> 
  ggplot(aes(x = rounds)) +
  geom_histogram(binwidth = 1000) +
  labs(x = "Rounds Played", y = "Number of Players") +
  theme_classic()
```

@@

## Impacts of an individual on team performance {#sec-discussion-1}
As seen in @sec-results, some of the predictors we chose, K/D, HS%, and total rounds played, are positively correlated with win rate
whereas ADR is unexpectedly negatively correlated with win rate. In a game where killing all members of the enemy team is a win condition,
it is clear that individual metrics such as K/D are an important part of a team's overall performance.
However, it is also obvious that a team's performance can not purely be explained by an individual's stats.

*CS* is a team game, every individual has 4 teammates they must work with to win. But even considering every numerical stat for all team members is not
sufficient to fully determine a team's success. Similar to physical sports, there are too many other factors to build a perfect model based only on hard numbers.
Every round of *CS* has many tactical decisions that must be made. Poor strategies and bad shotcalling can ruin a team's chances at winning while
good decision making and communication can make a player invaluable to a team.

For example, Finn "karrigan" Andersen currently plays on FaZe, a top ranking team having just won a large tournament, IEM Chengdu 2024.
On paper, karrigan is worse than the rest of his team and many of his competitors with a 0.89 K/D and 43.8% HS%, but he is the
IGL (in game leader) for FaZe. As IGL, he provides strategies and makes decisions for the rest of his team, allowing them to more effective.
Many other top *CS* teams also have IGLs, who will typically be older and have more experience, but have worse stats.

In summary, individual player stats can be a helpful way to predict their impact on a team's performance, but it never tells the full story.
This is applicable to *CS* as well as physical sports and other esports.

@@

As stated in @sec-discussion-1, *CS* is a team game and the current model attempts to predict a team's win rate based only on individual's stats.
This limits the predictive power of the model and a next step would be to include the remaining teammate's statistics in the model. 
This would allow us to predict win rates based on all the members of a team and would also allow us to see how players with different stats
interact and effect the team.

A team's win rate does not exist in a vacuum, it must play against another team. Currently, the model is not very useful as it only gives
an overall win rate. A much more useful model would give the win rate for a match against another team. A next step would be to include
the statistics of the enemy team's players in the model. This would allow us to see some of the interactions between teams and bring the model much closer
to something bookmakers and professional sports bettors would use.

One major flaw are the lifetime statistics. These help provide some ways to measure a player's performance but many of these may be
outdated, but are still included. Many players have been playing for years and their past performance may
no longer be relevant due changes to the game itself or age and declining physical abilities. The model could likely be improved by
limiting the lifetime statistics to more recent ones.

Finally, the current model uses only 4 predictors. Many other statistics could be added such as number of opening kills (first kill of the round) and opening deaths.
As stated in @sec-data for the explanation of @fig-hs, the HS% could be dependent on the weapons used, so weapons used could be included as an interaction variable.
